---
title: "Statistic Calculate Method"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW3 201811526 이은주
```{r echo=FALSE}
library(nycflights13)
library(tidyverse)
data(flights)
```

### 1. arrange() - p.18
(1) How could you use arrange() to sort all missing values (in dep_time) to the start?
```{r}
arrange(flights, desc(is.na(dep_time)))
```
is.na(dep_time) : NA는 TRUE(1)로 인식하고, NA가 아닌 경우 FALSE(0)로 인식한다.  
이때, 내림차순 정렬을 하여 1(NA)부터 정렬한다.

\pagebreak

(2) Sort flights to find the most delayed flights. Find the flights that left earliest.
```{r}
flights %>% arrange(desc(dep_delay))
flights %>% arrange(dep_delay)
```
내림차순 정렬(desc)을 통해 가장 지연된 비행기부터 정렬할 수 있다.  
오름차순 정렬에 따르면 가장 일찍 떠난 비행기는 97번이다.

\pagebreak

(3) Sort flights to find the fastest (highest speed) flights.
```{r}
flights %>% arrange(air_time) %>% select(air_time, flight, everything())
```
4368, 4631 flight이 air_time이 20분으로 fatest flights이다.

\pagebreak

(4) Which flights traveled the farthest? Which traveled the shortest?
```{r}
(fli_dist = flights %>% arrange(distance) %>% select(distance, flight, everything()))
fli_dist[1,] #shortest
fli_dist[dim(fli_dist)[1],] #farthest
```
shortest flight : 1632, farthest flight : 51

\pagebreak

### 2. select() - p.22
(1) 
```{r}
flights %>% select(dep_time, dep_delay, arr_time, arr_delay)
flights %>% select(starts_with("dep"), starts_with("arr"))
flights %>% select(matches("dep_(.)"), matches("arr_(.)"))
```

\pagebreak

(2) What happens if you include the name of a variable multiple times in a select() call?
```{r}
flights %>% select(dep_time, arr_time, dep_time)
```
반복하여 변수명을 포함할 시, 뒤의 변수는 무시한다.


(3) What does the one_of() function do? Why might it be helpful in conjunction with this vector?
```{r}
?select #all_of(), any_of()
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
flights %>% select(one_of(vars))
```
all_of, any_of : Matches variable names in a character vector  
one_of : all_of, any_of의 상위버전

\pagebreak

(4) Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
```{r}
select(flights, contains("time"))
select(flights, contains("TIME"))
select(flights, contains("TIME", ignore.case=FALSE))
```
select()는 변수명의 대문자, 소문자 구분을 하지 않는다.  
이때, inore.case=FALSE 옵션을 추가하면 대소문자를 구분한다.


