---
title: "Trial"
author: "EunJu Lee"
date: "2021-03-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## R Markdown
<!-- 이부분은 표시되지 않는다(shift+ctrl+c) -->
한글로 보고서=> html형식은 가능하나 pdf형식은 불가능(오류)  
또는 html-> open in browser-> pdf로 인쇄

This is an **R Markdown** document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure) 
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent **printing** of the R code that generated the plot.

## Including dataframe
```{r, echo=FALSE}
#echo=FALSE는 코드X 결과O
A = c("a","a", "b","b")
B = c(5,10,15,20)
dataframe= data.frame(A,B)
#plot(dataframe)
```

## Load the .csv file
```{r, eval=FALSE}
#eval=FALSE는 r코드는 쓰지만, 코드만 보여주고 작동(계산)시키지 않는다.  
dataframe = read.csv("~~")
```

```{r, include =FALSE}
#include=FALSE는코드를 아예 사용하지 않는다.  
dataframe = data.frame(A,B)
#plot(dataframe)
```

## Kable() function from knitr packages
```{r}
library(knitr)
kable(dataframe, digits=2)
```

## Malnually creating tables
|Plant|Temp|Growth|
|:----|:---:|----:|
|A    |20   |40   |

I'm `happy`.  
I'm *happy*.






